Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-05-26 paper.tex
Added screenshot of visual artifact with Boolean XOR (ref #14)
Mention figure of artifact right after bringing it up (ref #14)
Figure showing problem with pieces in perspective (ref #14)

Unfortunately the Boolean XOR approach may show some visual artifacts from
certain angles.  This occurs because when two pieces have the same depth value,
due to perspective one of the pieces may actually appear behind the other.  In
the future, this issue may be solved by using the distance from the camera to
sort rather than the actual depth.

% Picture of visual artifacts with Boolean XOR approach

% Picture of depth-sorting issue

>>>>

Unfortunately the Boolean XOR approach may show some visual artifacts from
certain angles.  Figure \ref{boolean-xor-with-artifact} shows an example of the
artifact.  This occurs because when two pieces have the same depth value, due to
perspective one of the pieces may actually appear behind the other, as
illustrated in figure \ref{pieces-in-perspective}.  In the future, this issue
may be solved by using the distance from the camera to sort rather than the
actual depth.

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-xor-screenshot-3.png}
\caption{Screenshot of Boolean XOR with visual artifact.}
\label{boolean-xor-with-artifact}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{pieces-in-perspective.pdf}
\caption{Top-down view of two pieces in perspective.  Notice how even though
both pieces have the same depth, a small sliver of the blue piece on the left
ends up being rendered behind the red piece on the right.}
\label{pieces-in-perspective}
\end{figure}
